---
#title: "TFM"
author: "Nombre Completo Autor"
date: "27/10/2017"
documentclass: book
classoption: a4paper
#classoption: a4paper,oneside
#bibliography: bib/library.bib
bibliography: ["bib/library.bib", "bib/paquetes.bib"]
#csl: methods-in-ecology-and-evolution.csl
csl: acm-sig-proceedings-long-author-list.csl
urlcolor: blue #black
linkcolor: blue #black
link-citations: yes
fontsize: 12pt # 10pt,11pt
geometry: margin = 2.5cm
output: 
  pdf_document: 
    keep_tex: no
    number_sections: yes
#    toc: yes
    fig_caption: yes
    includes:
      in_header: latex/latex_preambulo.tex
      before_body: portadas/latex_paginatitulo_modTFE.tex
#      before_body: portadas/latex_paginatitulo_modTFGE.tex
#      before_body: portadas/latex_paginatitulo_modTFGM.tex
#      before_body: portadas/latex_paginatitulo_modTFDGME.tex
#      before_body: portadas/latex_paginatitulo_modTFMDS.tex
#      before_body: portadas/latex_paginatitulo_mod_OV01.tex
      after_body: latex/latex_antes_enddoc.tex
---

---
nocite: | 
  @R-knitr,@R-rmarkdown,@R-dplyr,@R-ggplot2, @R-xtable,
  @R-stringr,@Techopedia,@Pentaho2
...


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'figurasR/',
                      echo = FALSE, warning = FALSE, message = FALSE,
                      fig.pos="H",fig.align="center",out.width="95%",
                      cache=FALSE)

knitr::write_bib(c("knitr","rmarkdown","dplyr","ggplot2","xtable",
                   "stringr","shiny","flexdashboard","htmlwidgets","bookdown"),
                 file="bib/paquetes.bib", width = 60)
```



\pagestyle{fancy}
\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\pagenumbering{roman}

\setcounter{tocdepth}{4}
\tableofcontents


\cleardoublepage   
<!--  \clearpage -->
\section*{Agradecimientos}
\addcontentsline{toc}{section}{Agradecimientos}

```{r child = 'agradecimientos.Rmd'}
```


\cleardoublepage   
<!--  \clearpage -->
\section*{Resumen}
\addcontentsline{toc}{section}{Resumen}

```{r child = 'resumen.Rmd'}
```


\clearpage
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

```{r child = 'abstract.Rmd'}
```


\cleardoublepage   
<!--  \clearpage -->
\listoffigures
\addcontentsline{toc}{section}{Índice de Figuras}

\cleardoublepage   
<!--  \clearpage -->
\listoftables
\addcontentsline{toc}{section}{Índice de Cuadros}


\cleardoublepage   
<!--  \clearpage -->
\pagenumbering{arabic}

\fancyhead[LE,RO]{\scriptsize\rightmark}
\fancyfoot[LO,RE]{\scriptsize\slshape \leftmark}
\fancyfoot[C]{}
\fancyfoot[LE,RO]{\footnotesize\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}


```{r child = 'capitulo01.Rmd'}
```

\FloatBarrier

```{r child = 'capitulo02.Rmd'}
```

\FloatBarrier

```{r child = 'capitulo03.Rmd'}
```

\FloatBarrier

```{r child = 'capitulo04.Rmd'}
```

\FloatBarrier

\appendix

```{r child = 'apendice01.Rmd'}
```



```{r child = 'apendice02.Rmd'}
```


\FloatBarrier
\cleardoublepage   
<!--  \clearpage -->

\fancyhead[CO,CE]{Bibliografía}

# Bibliografía
